---
title: "Create a point map"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Create a point map}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

## Description of generating a few point maps

The package can generate a simple point map with one or more
layers. First we can get the sample data:

```{r}
library(svis)
## Get the sample data
pts <- sample_data()

## This is a SpatialPointsDataFrame and then then be ploted with the sp package
library(sp)
plot(pts)
```

This data also contains covariates in the `pts@data` slot , which describes
each point in the data.

```{r}
str(pts@data[,1:7])
```

The map contains a function that runs on each feature that returns a popuptext.
We need to define this in the data as a variable named `pts@data$popup_text`.
We will put the Status of the dot in that variable so we can see that text
in the map popup.

```{r}
pts@data$popup_text <- pts@data$Status
head(pts@data$Status)
```

To plot this data we need to convert it to geojson.

```{r}
a <- convert_to_geojson(pts)
```

### Make a point make with one layer
Now we can make a layer with those points and put it in a map

```{r}
## Convert to layer object
layer <- point_layer(a)

## Generate the page header
header <- page_header()

## Map with a single layer:
body <- page_body(map_div(layer))
page <- page_page(header, body)
map <- tempfile(fileext = "html")
capture.output(page, file = map)
```

Then view the page
```{r eval = FALSE}
browseURL(map)
```

```{r results = 'html', echo = FALSE}

## Tricky here: During the build of thé vignette, I place the map file
## in the do folder. Then include it in an iframe as the basename(map)
## because when you view the vignette you are working in the local
## dir.
map <- "../inst/doc/map1.html"
capture.output(page, file = map)
knitr::include_url(basename(map), height = "1000px")
```

### Make a point map with several layers

```{r}
## The first layer
pts <- sample_data("cwd")
pts@data$popup_text <- pts@data$Status
a <- convert_to_geojson(pts)

## And a second layer
pts2 <- sample_data("asf")
## Add some popup text
pts2@data$popup_text <- paste(pts2@data$Kön, pts2@data$Status)
b <- convert_to_geojson(pts2)
```

Now we can make a layer with those points and put it in a map

```{r}
## Convert to layer objects with 2 different names:
layer1 <- point_layer(a, layer_title = "CWD")
layer2 <- point_layer(b, layer_title = "ASF", fillColor = shQuote("#ff0000"))
layersob <- layers(list(layer1, layer2))

## Generate the page header
header <- page_header()

## Map with a single layer:
body <- page_body(map_div(layersob))
page <- page_page(header, body)
map <- tempfile(fileext = "html")
capture.output(page, file = map)
```

Then view the page
```{r eval = FALSE}
browseURL(map)
```

```{r results = 'html', echo = FALSE}
map <- "../inst/doc/map2.html"
capture.output(page, file = map)
knitr::include_url(basename(map), height = "1000px")
```

### Make a map with multiple colours based on a variable
